---
title: "Causal Distillation Trees"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

COLORS <- c(
  "Distilled Rboost" = "#6aafe4",
  "Distilled Causal Forest" = "#1f5d8f",
  "Distilled BCF" = "#1c3145",
  "Distilled Rspline" = "#93ACBF",
  "Virtual Twins" = "#768c50",
  "Causal Tree" = "#953a2f",
  "Linear Regression" = "#b2954a",
  "Lasso" = "#D2BE90"
)
CROSSFIT_COLORS <- c(
  "#981643", "#ED724F", "#F8B06E", "#FCE096", "#8FB989", "#4287B7", "#5E519B"
)
RULEFIT_COLORS <- c(
  "CART" = "#1f5d8f",
  "Rulefit (linear + rules, max depth = 3)" = "#FF9300",
  "Rulefit (linear + rules, max depth = 2)" = "#E7298A",
  "Rulefit (rules only, max depth = 3)" = "#66A61E",
  "Rulefit (rules only, max depth = 2)" = "#7570B3"
)
LINE_TYPES <- c(
  "Pruned" = "solid",
  "Unpruned" = "dashed"
)

HERITABILITY_LABS <- list(
  "0.2" = "Weak (0.2)",
  "0.6" = "Moderate (0.6)",
  "1" = "Strong (1)"
)
CORR_LABS <- list(
  "0.1" = "Weak (0.1)",
  "0.5" = "Moderate (0.5)",
  "0.9" = "Strong (0.9)"
)
signal_labeller <- function(labels) {
  labellers <- list(
    tau_heritability = HERITABILITY_LABS,
    .X_corr = CORR_LABS
  )
  for (var in names(labels)) {
    if (var %in% names(labellers)) {
      labels[[var]] <- unname(
        labellers[[var]][as.character(labels[[var]])]
      )
    }
  }
  labels
}

add_pruned_column <- function(data) {
  data |> 
    dplyr::mutate(
      .is_pruned = dplyr::case_when(
        stringr::str_detect(.method_name, "unpruned") ~ "Unpruned",
        TRUE ~ "Pruned"
      ),
      .method_name = stringr::str_remove(.method_name, " \\(unpruned\\)")
    )
}

RESULTS_DIR <- here::here("results")
FIG_DIR <- here::here("results", "figures")
if (!dir.exists(FIG_DIR)) {
  dir.create(FIG_DIR, recursive = TRUE)
}
```

# Simulations {.tabset .tabset-vmodern}

```{r}
here::i_am("notebooks/paper_figures.Rmd")
EXP_NAME <- "Test"
for (fdir in here::here("R", c("dgp", "eval", "method", "viz"))) {
  for (fname in list.files(fdir, full.names = TRUE)) {
    source(fname, chdir = TRUE)
  }
}
source(here::here(file.path("meals", "setup.R")))
source(here::here(file.path("meals", "shared_dgps.R")))
source(here::here(file.path("meals", "shared_method_params.R")))
source(here::here(file.path("meals", "shared_methods.R")))
source(here::here(file.path("meals", "shared_evaluators.R")))
source(here::here(file.path("meals", "shared_visualizers.R")))
source(here::here(file.path("meals", "shared_experiments.R")))
experiment <- experiment |>
  add_dgp(gaussian_X_unbiased_Z_and) |>
  add_vary_across(
    .dgp = gaussian_X_unbiased_Z_and$name,
    tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
  )

example_experiment <- example_experiment |>
  add_dgp(gaussian_X_unbiased_Z_and) |>
  add_vary_across(
    .dgp = gaussian_X_unbiased_Z_and$name,
    n = c(100, 500, 1000, 2000)
  )

crossfit_experiment <- crossfit_experiment |>
  add_dgp(gaussian_X_unbiased_Z_and) |>
  add_vary_across(
    .dgp = gaussian_X_unbiased_Z_and$name,
    tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
  )

rulefit_experiment <- rulefit_experiment |> 
  add_dgp(gaussian_X_unbiased_Z_and) |>
  add_vary_across(
    .dgp = gaussian_X_unbiased_Z_and$name,
    tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
  )
```

## Example {.tabset .tabset-pills .tabset-pills-square}

```{r results = "asis"}
sim_results_dir <- file.path(RESULTS_DIR, "Main Simulations")
sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND with Linear Covariates DGP",
  "Additive with Linear Covariates DGP",
  "OR with Linear Covariates DGP"
)

keep_methods_ls <- list(
  "causal_tree_only" = c("Causal Tree"),
  "all_methods" = c("Distilled Causal Forest", "Causal Tree")
)

for (sim_name in sim_names) {
  fit_results <- readRDS(
    file.path(
      sim_results_dir, sim_name, "Varying n", "fit_results.rds"
    )
  )
  eval_results <- readRDS(
    file.path(
      sim_results_dir, sim_name, "Varying n", "eval_results.rds"
    )
  )
  viz_results <- visualize_experiment(
    example_experiment, fit_results, eval_results
  )
  true_nsubgroups <- dplyr::case_when(
    stringr::str_detect(sim_name, "Additive") ~ 4,
    stringr::str_detect(sim_name, "AND") ~ 3,
    stringr::str_detect(sim_name, "OR") ~ 6
  )
  hlines_df <- tibble::tibble(
    .metric = c(
      "Number of Subgroups", "# True Positives", "# False Positives"
    ) |> forcats::fct_inorder(),
    yint = c(true_nsubgroups, 2, 0)
  )
  for (keep_methods_idx in 1:length(keep_methods_ls)) {
    keep_methods <- keep_methods_ls[[keep_methods_idx]]
    keep_methods_name <- names(keep_methods_ls)[keep_methods_idx]
    plt <- viz_results$`Number of Subgroups Plot`
    plt$data <- plt$data |> 
      dplyr::filter(
        .method_name %in% !!keep_methods
      )
    plt <- plt +
      ggplot2::geom_hline(
        ggplot2::aes(yintercept = yint),
        data = hlines_df,
        inherit.aes = FALSE,
        color = "darkgray",
        linetype = "dashed"
      ) +
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98")
      )
    ggplot2::ggsave(
      plt, 
      filename = file.path(
        FIG_DIR, 
        sprintf("%s sim_example_nsubgroup_%s.pdf", sim_name, keep_methods_name)
      ),
      height = 3.1,
      width = 11.5
    )
  }
}
```

## Main Simulations {.tabset .tabset-pills .tabset-pills-square}

```{r results = "asis"}
sim_results_dir <- file.path(RESULTS_DIR, "Main Simulations")
SIM_NAMES <- c(
  "AND DGP" = "AND DGP",
  "Additive DGP" = "Additive DGP",
  "OR DGP" = "OR DGP",
  "AND with Linear Covariates DGP" = "AND DGP with Linear Covariates",
  "Additive with Linear Covariates DGP" = "Additive DGP with Linear Covariates",
  "OR with Linear Covariates DGP" = "OR DGP with Linear Covariates"
)

# load in results
eval_results_ls <- list()
viz_results_ls <- list()
for (sim_name in names(SIM_NAMES)) {
  print(sim_name)
  experiment <- readRDS(
    file.path(
      sim_results_dir, sim_name, "Varying tau_heritability", "experiment.rds"
    )
  )
  fit_results <- get_cached_results(experiment, "fit")
  eval_results <- get_cached_results(experiment, "eval")
  viz_results <- visualize_experiment(experiment, fit_results, eval_results)
  eval_results_ls[[SIM_NAMES[[sim_name]]]] <- eval_results
  viz_results_ls[[SIM_NAMES[[sim_name]]]] <- viz_results
}
```

### Selected Subgroup Features + Threshold Distances + Estimated Subgroup ATEs

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Causal Forest",
  "Distilled BCF",
  "Distilled Rspline",
  "Virtual Twins",
  "Causal Tree",
  "Linear Regression",
  "Lasso"
)

## without covariates
sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP"
)
plt <- purrr::map(
  sim_names,
  function(sim_name) {
    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_selection <- plt
    
    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_cate <- plt +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12),
        legend.title = ggplot2::element_text(face = "bold", size = 16),
        legend.text = ggplot2::element_text(size = 12)
      )
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X1"
      )
    plt_thr1 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(1), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X2"
      )
    plt_thr2 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(2), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    plt_thr <- plt_thr1 + plt_thr2
    
    plt <- patchwork::wrap_plots(
      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
      widths = c(3.5, 2.35, 1)
    ) &
      ggplot2::labs(x = NULL) &
      ggplot2::theme(
        legend.position = "bottom",
        legend.box.margin = ggplot2::margin(t = 10, r = 0, b = 0, l = 0)
      )
    
    if (sim_name != sim_names[3]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none", linetype = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[3] ~ 0.66
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.03, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1, 
          margin = ggplot2::margin(b = 16)
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    if (sim_name == sim_names[3]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors.pdf"),
  height = 9.5, 
  width = 15
)

## with covariates
sim_names <- c(
  "AND DGP with Linear Covariates",
  "Additive DGP with Linear Covariates",
  "OR DGP with Linear Covariates"
)
plt <- purrr::map(
  sim_names,
  function(sim_name) {
    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_selection <- plt
    
    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_cate <- plt +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12),
        legend.title = ggplot2::element_text(face = "bold", size = 16),
        legend.text = ggplot2::element_text(size = 12)
      )
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X1"
      )
    plt_thr1 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(1), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X2"
      )
    plt_thr2 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(2), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    plt_thr <- plt_thr1 + plt_thr2
    
    plt <- patchwork::wrap_plots(
      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
      widths = c(3.5, 2.35, 1)
    ) &
      ggplot2::labs(x = NULL) &
      ggplot2::theme(
        legend.position = "bottom",
        legend.box.margin = ggplot2::margin(t = 10, r = 0, b = 0, l = 0)
      )
    
    if (sim_name != sim_names[3]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none", linetype = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[3] ~ 0.66
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.08, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    if (sim_name == sim_names[3]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_cov.pdf"),
  height = 9.5, 
  width = 15
)
```

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Causal Forest",
  "Distilled BCF",
  "Distilled Rspline",
  "Virtual Twins",
  "Causal Tree (cp = 1E-4)",
  "Linear Regression",
  "Lasso"
)

## without covariates
sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND DGP with Linear Covariates",
  "Additive DGP with Linear Covariates",
  "OR DGP with Linear Covariates"
)
plt <- purrr::map(
  sim_names,
  function(sim_name) {
    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_selection <- plt
    
    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_cate <- plt +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12),
        legend.title = ggplot2::element_text(face = "bold", size = 16),
        legend.text = ggplot2::element_text(size = 12)
      )
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X1"
      )
    plt_thr1 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(1), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X2"
      )
    plt_thr2 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(2), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    plt_thr <- plt_thr1 + plt_thr2
    
    plt <- patchwork::wrap_plots(
      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
      widths = c(3.5, 2.35, 1)
    ) &
      ggplot2::labs(x = NULL) &
      ggplot2::theme(
        legend.position = "bottom",
        legend.box.margin = ggplot2::margin(t = 10, r = 0, b = 0, l = 0)
      )
    
    if (sim_name != sim_names[6]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none", linetype = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[6] ~ 0.66,
      TRUE ~ 0.5
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    if (sim_name %in% sim_names[1:3]) {
      tag_pos_y <- -0.03
    } else {
      tag_pos_y <- -0.08
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(tag_pos_y, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1, 
          margin = ggplot2::margin(b = 16)
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    if (sim_name == sim_names[6]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_oracle.pdf"),
  height = 17, 
  width = 15
)
```

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Rboost (unpruned)",
  "Distilled Causal Forest",
  "Distilled Causal Forest (unpruned)",
  "Distilled BCF",
  "Distilled BCF (unpruned)",
  "Distilled Rspline",
  "Distilled Rspline (unpruned)",
  "Causal Tree",
  "Causal Tree (unpruned)"
)

sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND DGP with Linear Covariates",
  "Additive DGP with Linear Covariates",
  "OR DGP with Linear Covariates"
)
plt <- purrr::map(
  sim_names,
  function(sim_name) {
    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      ) |> 
      add_pruned_column()
    plt$layers[[1]]$mapping <- ggplot2::aes(
      x = tau_heritability, 
      ymin = mean_feature_selection_err - se_feature_selection_err,
      ymax = mean_feature_selection_err + se_feature_selection_err,
      fill = .method_name,
      group = interaction(.method_name, .is_pruned)
    )
    plt$layers[[2]]$mapping <- ggplot2::aes(
      x = tau_heritability, 
      y = mean_feature_selection_err,
      color = .method_name,
      linetype = .is_pruned, 
      group = interaction(.method_name, .is_pruned)
    )
    plt_selection <- plt +
      ggplot2::scale_linetype_manual(
        values = LINE_TYPES
      ) +
      ggplot2::guides(
        linetype = ggplot2::guide_legend(keywidth = ggplot2::unit(1, "cm"))
      )
    
    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      ) |> 
      add_pruned_column()
    plt$layers[[1]]$mapping <- ggplot2::aes(
      x = tau_heritability, 
      ymin = mean_ate_err - se_ate_err,
      ymax = mean_ate_err + se_ate_err,
      fill = .method_name,
      group = interaction(.method_name, .is_pruned)
    )
    plt$layers[[2]]$mapping <- ggplot2::aes(
      x = tau_heritability, 
      y = mean_ate_err,
      color = .method_name,
      linetype = .is_pruned, 
      group = interaction(.method_name, .is_pruned)
    )
    plt_cate <- plt +
      ggplot2::scale_linetype_manual(
        values = LINE_TYPES
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12),
        legend.title = ggplot2::element_text(face = "bold", size = 16),
        legend.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(
        linetype = ggplot2::guide_legend(keywidth = ggplot2::unit(1, "cm"))
      )
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X1"
      ) |> 
      add_pruned_column()
    plt$layers[[1]]$mapping <- ggplot2::aes(
      x = tau_heritability, 
      ymin = mean_threshold_dist - se_threshold_dist,
      ymax = mean_threshold_dist + se_threshold_dist,
      fill = .method_name,
      group = interaction(.method_name, .is_pruned)
    )
    plt$layers[[2]]$mapping <- ggplot2::aes(
      x = tau_heritability, 
      y = mean_threshold_dist,
      color = .method_name,
      linetype = .is_pruned, 
      group = interaction(.method_name, .is_pruned)
    )
    plt_thr1 <- plt +
      ggplot2::scale_linetype_manual(
        values = LINE_TYPES
      ) +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(1), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X2"
      ) |> 
      add_pruned_column()
    plt$layers[[1]]$mapping <- ggplot2::aes(
      x = tau_heritability, 
      ymin = mean_threshold_dist - se_threshold_dist,
      ymax = mean_threshold_dist + se_threshold_dist,
      fill = .method_name,
      group = interaction(.method_name, .is_pruned)
    )
    plt$layers[[2]]$mapping <- ggplot2::aes(
      x = tau_heritability, 
      y = mean_threshold_dist,
      color = .method_name,
      linetype = .is_pruned, 
      group = interaction(.method_name, .is_pruned)
    )
    plt_thr2 <- plt +
      ggplot2::scale_linetype_manual(
        values = LINE_TYPES
      ) +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(2), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    plt_thr <- plt_thr1 + plt_thr2
    
    plt <- patchwork::wrap_plots(
      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
      widths = c(3.5, 2.35, 1)
    ) &
      ggplot2::labs(x = NULL) &
      ggplot2::theme(
        legend.position = "bottom"
      )
    
    if (sim_name != sim_names[length(sim_names)]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none", linetype = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[6] ~ 0.65,
      TRUE ~ 0.5
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    if (stringr::str_detect(sim_name, "with")) {
      tag_x_pos <- -.08
    } else {
      tag_x_pos <- -.03
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(tag_x_pos, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      ) &
      ggplot2::labs(linetype = "Pruning Mode")
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.78, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    if (sim_name == sim_names[length(sim_names)]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 1.9, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_all_with_pruning.pdf"),
  height = 17, 
  width = 14
)
```

### Selected Subgroup Features + Threshold Distances + Estimated Subgroup ATEs (max depth = 2)

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Causal Forest",
  "Distilled BCF",
  "Distilled Rspline",
  "Virtual Twins",
  "Causal Tree",
  "Linear Regression",
  "Lasso"
)

sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND DGP with Linear Covariates",
  "Additive DGP with Linear Covariates",
  "OR DGP with Linear Covariates"
)
plt <- purrr::map(
  sim_names,
  function(sim_name) {
    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot (max depth = 2)`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_selection <- plt
    
    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot (max depth = 2)`
    linear_data <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`$data |> 
      dplyr::filter(
        .method_name %in% c("Linear Regression", "Lasso")
      )
    plt$data <- plt$data |>
      dplyr::filter(
        !(.method_name %in% c("Linear Regression", "Lasso"))
      ) |>
      dplyr::bind_rows(linear_data) |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_cate <- plt +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12),
        legend.title = ggplot2::element_text(face = "bold", size = 16),
        legend.text = ggplot2::element_text(size = 12)
      )
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot (max depth = 2)`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X1"
      )
    plt_thr1 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(1), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot (max depth = 2)`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X2"
      )
    plt_thr2 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(2), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    plt_thr <- plt_thr1 + plt_thr2
    
    plt <- patchwork::wrap_plots(
      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
      widths = c(3.5, 2.35, 1)
    ) &
      ggplot2::labs(x = NULL) &
      ggplot2::theme(
        legend.position = "bottom",
        legend.box.margin = ggplot2::margin(t = 6, r = 0, b = 0, l = 0)
      )
    
    if (sim_name != sim_names[length(sim_names)]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none", linetype = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[6] ~ 0.7,
      TRUE ~ 0.5
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features\n(max depth = 2)"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds\n(max depth = 2)"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs\n(max depth = 2)"
        )
    }
    if (stringr::str_detect(sim_name, "with")) {
      tag_x_pos <- -.08
    } else {
      tag_x_pos <- -.03
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(tag_x_pos, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.78, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    if (sim_name == sim_names[length(sim_names)]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 1.95, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_all_max_depth2.pdf"),
  height = 17, 
  width = 14
)
```

### Threshold Distributions

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Causal Forest",
  "Distilled BCF",
  "Distilled Rspline",
  "Virtual Twins",
  "Causal Tree",
  "Linear Regression",
  "Lasso"
)
KEEP_HERITABILITY <- c(0.2, 0.6, 1)

sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND DGP with Linear Covariates",
  "Additive DGP with Linear Covariates",
  "OR DGP with Linear Covariates"
)
plt <- purrr::imap(
  sim_names,
  function(sim_name, idx) {
    tag <- LETTERS[idx]
    plt <- viz_results_ls[[sim_name]]$`Subgroup Thresholds Distribution Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY
      ) |>
      dplyr::mutate(
        .method_name = factor(.method_name, levels = KEEP_METHODS)
      )
    plt <- plt +
      ggplot2::facet_grid(.var ~ tau_heritability, labeller = signal_labeller) +
      ggplot2::labs(
        title = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5
        )
      )
    if (stringr::str_detect(sim_name, "with")) {
      plt <- plt +
        ggplot2::labs(y = "")
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 2, guides = "collect", byrow = FALSE
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_thresholds_all.pdf"),
  height = 10, 
  width = 13
)
```

### Subgroup Stability

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Causal Forest",
  "Distilled BCF",
  "Distilled Rspline",
  "Causal Tree"
)
KEEP_HERITABILITY <- c(0.2, 0.6, 1)

sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND DGP with Linear Covariates",
  "Additive DGP with Linear Covariates",
  "OR DGP with Linear Covariates"
)

plt <- purrr::map(
  sim_names,
  function(sim_name) {
    f1_df <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`$data |> 
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY,
        .metric == "F1"
      ) |> 
      dplyr::mutate(
        .method_name = factor(.method_name, levels = KEEP_METHODS),
        .value = mean_feature_selection_err
      )
    cate_df <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY,
        .metric == "rmse"
      ) |> 
      dplyr::mutate(
        .method_name = factor(.method_name, levels = KEEP_METHODS),
        .metric = "Subgroup\nATE RMSE",
        .value = mean_ate_err
      )
    
    plt_err <- dplyr::bind_rows(f1_df, cate_df) |> 
      dplyr::mutate(
        .metric = forcats::fct_inorder(.metric)
      ) |> 
      ggplot2::ggplot() +
      ggplot2::aes(
        x = .method_name,
        y = .value, 
        fill = .method_name
      ) +
      ggplot2::geom_bar(
        stat = "identity", size = 1, width = 0.75
      ) +
      ggplot2::scale_color_manual(
        breaks = KEEP_METHODS,
        values = COLORS
      ) +
      ggplot2::scale_fill_manual(
        breaks = KEEP_METHODS,
        values = COLORS
      ) +
      ggplot2::facet_grid(
        .metric ~ tau_heritability, labeller = signal_labeller, 
        scales = "free_y", switch = "y"
      ) +
      ggplot2::scale_x_discrete(
        breaks = KEEP_METHODS,
        labels = stringr::str_replace_all(KEEP_METHODS, " ", "\n")
      ) +
      ggplot2::labs(y = "", x = "Method") +
      ggplot2::guides(color = "none", fill = "none") +
      vthemes::theme_vmodern(size_preset = "medium", grid_color = "grey98") +
      ggplot2::theme(
        strip.background.y = ggplot2::element_blank(),
        strip.text.y = ggplot2::element_text(
          color = "black", size = 16
        ),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_blank(),
        axis.text.y = ggplot2::element_text(size = 9)
      )
    
    plt <- viz_results_ls[[sim_name]]$`Subgroup Stability Diagnostics Plot`[[1]]
    plt$data <- plt$data |> 
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY
      ) |> 
      dplyr::mutate(
        .metric = "Jaccard SSI"
      )
    plt_jaccard <- plt +
      ggplot2::geom_line(size = 0.75) +
      ggplot2::facet_grid(
        ~ tau_heritability, labeller = signal_labeller, switch = "y"
      ) +
      ggplot2::coord_cartesian(xlim = c(1, 4)) +
      ggplot2::scale_x_continuous(
        breaks = 1:4
      ) +
      ggplot2::scale_y_continuous(
        limits = c(0, 1), breaks = seq(0, 1, by = 0.2)
      ) +
      vthemes::theme_vmodern(size_preset = "medium") +
      ggplot2::theme(
        strip.background.y = ggplot2::element_blank(),
        strip.text.y = ggplot2::element_text(
          color = "black", size = 16
        ),
        strip.placement = "outside",
        axis.text.y = ggplot2::element_text(size = 9)
      )
    
    plt <- patchwork::wrap_plots(
      plt_jaccard, plt_err,
      ncol = 1, heights = c(1.2, 2), guides = "collect"
    ) +
      patchwork::plot_layout(
        axis_titles = "collect_x"
      ) +
      patchwork::plot_annotation(
        title = sim_name, 
        tag_levels = "A", 
        tag_prefix = "(",
        tag_suffix = ")",
        theme = ggplot2::theme(
          plot.title = ggplot2::element_text(
            size = 18, face = "italic", hjust = 0.42
          )
        )
      ) &
      ggplot2::theme(
        # legend.position = "bottom",  # for slides
        plot.tag = ggplot2::element_text(size = 16)
      )
    # ggplot2::ggsave(
    #   plt, 
    #   filename = file.path(
    #     FIG_DIR, 
    #     sprintf("sim_stability_%s_slides.pdf", sim_name)
    #   ),
    #   width = 11.5,
    #   height = 9
    # )
    ggplot2::ggsave(
      plt, 
      filename = file.path(
        FIG_DIR,
        sprintf("sim_stability_%s.pdf", sim_name)
      ),
      width = 12,
      height = 7.5
    )
  }
)
```

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Causal Forest",
  "Distilled BCF",
  "Distilled Rspline",
  "Causal Tree"
)
KEEP_HERITABILITY <- c(0.2, 0.6, 1)

sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND DGP with Linear Covariates",
  "Additive DGP with Linear Covariates",
  "OR DGP with Linear Covariates"
)

plt <- purrr::map(
  sim_names,
  function(sim_name) {
    plt_df <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`$data |> 
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY,
        .metric == "F1"
      ) |>
      dplyr::mutate(
        .method_name = factor(.method_name, levels = KEEP_METHODS)
      )
    plt_f1 <- plt_df |> 
      ggplot2::ggplot() +
      ggplot2::aes(
        x = .method_name,
        y = mean_feature_selection_err,
        fill = .method_name
      ) +
      ggplot2::geom_bar(stat = "identity", size = 1) +
      ggplot2::scale_color_manual(
        breaks = KEEP_METHODS,
        values = COLORS
      ) +
      ggplot2::scale_fill_manual(
        breaks = KEEP_METHODS,
        values = COLORS
      ) +
      ggplot2::facet_grid(
        tau_heritability ~ ., labeller = signal_labeller, scales = "free_y"
      ) +
      ggplot2::labs(y = "F1", x = "Method") +
      ggplot2::guides(color = "none", fill = "none") +
      vthemes::theme_vmodern(size_preset = "medium", grid_color = "grey98") +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        axis.text.x = ggplot2::element_text(angle = 90, hjust = 1, vjust = 0.5)
      )
    
    plt_df <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY,
        .metric == "rmse"
      ) |>
      dplyr::mutate(
        .method_name = factor(.method_name, levels = KEEP_METHODS),
      )
    plt_cate <- plt_df |> 
      ggplot2::ggplot() +
      ggplot2::aes(
        x = .method_name,
        y = mean_ate_err,
        fill = .method_name
      ) +
      ggplot2::geom_bar(stat = "identity", size = 1) +
      ggplot2::scale_color_manual(
        breaks = KEEP_METHODS,
        values = COLORS
      ) +
      ggplot2::scale_fill_manual(
        breaks = KEEP_METHODS,
        values = COLORS
      ) +
      ggplot2::facet_grid(
        tau_heritability ~ ., labeller = signal_labeller, scales = "free_y"
      ) +
      ggplot2::labs(y = "Subgroup ATE RMSE", x = "Method") +
      ggplot2::guides(color = "none", fill = "none") +
      vthemes::theme_vmodern(size_preset = "medium", grid_color = "grey98") +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        axis.text.x = ggplot2::element_text(angle = 90, hjust = 1, vjust = 0.5)
      )
      
    plt <- viz_results_ls[[sim_name]]$`Subgroup Stability Diagnostics Plot`[[1]]
    plt$data <- plt$data |> 
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY
      )
    plt_jaccard <- plt +
      ggplot2::geom_line(size = 0.75) +
      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
      ggplot2::coord_cartesian(xlim = c(1, 4)) +
      ggplot2::scale_x_continuous(
        breaks = 1:4
      ) +
      ggplot2::scale_y_continuous(
        limits = c(0, 1), breaks = seq(0, 1, by = 0.2)
      ) +
      vthemes::theme_vmodern(size_preset = "medium")
    
    plt <- viz_results_ls[[sim_name]]$`Subgroup Stability Diagnostics Plot`[[2]]
    plt$data <- plt$data |> 
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY
      ) |>
      dplyr::mutate(
        .method_name = factor(.method_name, levels = KEEP_METHODS)
      )
    FT_COLORS <- c(
      "#d3831b", "#eeb062",
      "#CCCCCC", "#B5B5B5", "#9E9E9E", "#888888",
      "#717171", "#5A5A5A", "#434343", "#2D2D2D"
    )
    plt_stability_feature <- plt +
      ggplot2::scale_fill_manual(values = FT_COLORS) +
      ggplot2::facet_grid(tau_heritability ~ depth, labeller = signal_labeller) +
      vthemes::theme_vmodern(size_preset = "medium") +
      ggplot2::theme(
        axis.text.x = ggplot2::element_text(angle = 90, hjust = 1, vjust = 0.5)
      )
    
    plt <- patchwork::wrap_plots(
      plt_f1, plt_cate, plt_jaccard, plt_stability_feature,
      nrow = 1, widths = c(0.5, 0.5, 1.25, 3.25), guides = "collect"
    ) |> 
      patchwork::wrap_elements() +
      ggplot2::labs(
        title = "   (A) Subgroup Estimation       (B) Jaccard Stability                              (C) Feature Stability",
        tag = sim_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 20, face = "bold", hjust = 0.5
        ),
        plot.tag.position = c(0.47, 1.02),
        plot.margin = ggplot2::unit(c(0.32, 0, 0, 0.2), units = "in"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0, vjust = -0.3
        )
      )
    
    ggplot2::ggsave(
      plt, 
      filename = file.path(
        FIG_DIR, 
        sprintf("sim_stability_feature_%s.pdf", sim_name)
      ),
      height = 8, 
      width = 14
    )
  }
)
```

### Number of Trees/Replicates Heatmap

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Rboost (unpruned)",
  "Distilled Causal Forest",
  "Distilled Causal Forest (unpruned)",
  "Distilled BCF",
  "Distilled BCF (unpruned)",
  "Distilled Rspline",
  "Distilled Rspline (unpruned)",
  "Virtual Twins",
  "Causal Tree",
  "Causal Tree (unpruned)",
  "Linear Regression",
  "Lasso"
)
KEEP_HERITABILITY <- c(0.2, 0.6, 1)

# without covariates
sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND DGP with Linear Covariates",
  "Additive DGP with Linear Covariates",
  "OR DGP with Linear Covariates"
)
plt <- purrr::imap(
  sim_names,
  function(sim_name, idx) {
    tag <- LETTERS[idx]
    plt <- viz_results_ls[[sim_name]]$`Feature and Split Frequency Plots`[[1]]
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY
      ) |>
      dplyr::mutate(
        .method_name = factor(.method_name, levels = rev(KEEP_METHODS))
      )
    plt <- plt +
      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
      ggplot2::labs(
        title = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5
        )
      )
    if (stringr::str_detect(sim_name, "with")) {
      plt <- plt + 
        ggplot2::labs(y = "")
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 2, guides = "collect", byrow = FALSE
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_ntrees.pdf"),
  height = 20, 
  width = 13.5
)
```

## Main Simulations (n = 1000) {.tabset .tabset-pills .tabset-pills-square}

```{r results = "asis"}
sim_results_dir <- file.path(RESULTS_DIR, "Main Simulations (n=1000)")
SIM_NAMES <- c(
  "AND DGP" = "AND DGP",
  "Additive DGP" = "Additive DGP",
  "OR DGP" = "OR DGP",
  "AND with Linear Covariates DGP" = "AND DGP with Linear Covariates",
  "Additive with Linear Covariates DGP" = "Additive DGP with Linear Covariates",
  "OR with Linear Covariates DGP" = "OR DGP with Linear Covariates"
)

# load in results
eval_results_ls <- list()
viz_results_ls <- list()
for (sim_name in names(SIM_NAMES)) {
  print(sim_name)
  experiment <- readRDS(
    file.path(
      sim_results_dir, sim_name, "Varying tau_heritability", "experiment.rds"
    )
  )
  fit_results <- get_cached_results(experiment, "fit")
  eval_results <- get_cached_results(experiment, "eval")
  viz_results <- visualize_experiment(experiment, fit_results, eval_results)
  eval_results_ls[[SIM_NAMES[[sim_name]]]] <- eval_results
  viz_results_ls[[SIM_NAMES[[sim_name]]]] <- viz_results
}
```

### Selected Subgroup Features + Threshold Distances + Estimated Subgroup ATEs

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Causal Forest",
  "Distilled BCF",
  "Distilled Rspline",
  "Virtual Twins",
  "Causal Tree",
  "Linear Regression",
  "Lasso"
)

## without covariates
sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP"
)
plt <- purrr::map(
  sim_names,
  function(sim_name) {
    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_selection <- plt
    
    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_cate <- plt +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12),
        legend.title = ggplot2::element_text(face = "bold", size = 16),
        legend.text = ggplot2::element_text(size = 12)
      )
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X1"
      )
    plt_thr1 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(1), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X2"
      )
    plt_thr2 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(2), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    plt_thr <- plt_thr1 + plt_thr2
    
    plt <- patchwork::wrap_plots(
      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
      widths = c(3.5, 2.35, 1)
    ) &
      ggplot2::labs(x = NULL) &
      ggplot2::theme(
        legend.position = "bottom",
        legend.box.margin = ggplot2::margin(t = 10, r = 0, b = 0, l = 0)
      )
    
    if (sim_name != sim_names[3]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none", linetype = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[3] ~ 0.66
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.03, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1, 
          margin = ggplot2::margin(b = 16)
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    if (sim_name == sim_names[3]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_n1000.pdf"),
  height = 9.5, 
  width = 15
)

## with covariates
sim_names <- c(
  "AND DGP with Linear Covariates",
  "Additive DGP with Linear Covariates",
  "OR DGP with Linear Covariates"
)
plt <- purrr::map(
  sim_names,
  function(sim_name) {
    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_selection <- plt
    
    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_cate <- plt +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12),
        legend.title = ggplot2::element_text(face = "bold", size = 16),
        legend.text = ggplot2::element_text(size = 12)
      )
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X1"
      )
    plt_thr1 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(1), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X2"
      )
    plt_thr2 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(2), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    plt_thr <- plt_thr1 + plt_thr2
    
    plt <- patchwork::wrap_plots(
      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
      widths = c(3.5, 2.35, 1)
    ) &
      ggplot2::labs(x = NULL) &
      ggplot2::theme(
        legend.position = "bottom",
        legend.box.margin = ggplot2::margin(t = 10, r = 0, b = 0, l = 0)
      )
    
    if (sim_name != sim_names[3]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none", linetype = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[3] ~ 0.66
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.08, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    if (sim_name == sim_names[3]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_cov_n1000.pdf"),
  height = 9.5, 
  width = 15
)
```

## Varying \# Repeated Crossfits Simulations {.tabset .tabset-pills .tabset-pills-square}

```{r results = "asis"}
sim_results_dir <- file.path(RESULTS_DIR, "Crossfitting Simulations")
SIM_NAMES <- c(
  "AND DGP" = "AND DGP",
  "Additive DGP" = "Additive DGP",
  "OR DGP" = "OR DGP"
)

# load in results
eval_results_ls <- list()
viz_results_ls <- list()
for (sim_name in names(SIM_NAMES)) {
  crossfit_experiment <- readRDS(
    file.path(
      sim_results_dir,
      paste0(sim_name, "-Distilled Rboost (crossfit)"), 
      "Varying tau_heritability-nreps_crossfit", "experiment.rds"
    )
  )
  fit_results <- get_cached_results(crossfit_experiment, "fit")
  eval_results <- get_cached_results(crossfit_experiment, "eval")
  eval_results <- purrr::map(
    eval_results,
    ~ .x |>
      dplyr::filter(
        !stringr::str_detect(.method_name, "unpruned"),
        !stringr::str_detect(.method_name, "Causal Forest")
      ) |>
      dplyr::mutate(
        .method_name = stringr::str_remove_all(.method_name, " \\(.*\\)"),
        nreps_crossfit = tidyr::replace_na(nreps_crossfit, 0) |>
          as.factor() |>
          forcats::fct_inseq()
      )
  )
  viz_results <- visualize_experiment(
    crossfit_experiment, fit_results, eval_results
  )
  eval_results_ls[[SIM_NAMES[[sim_name]]]] <- eval_results
  viz_results_ls[[SIM_NAMES[[sim_name]]]] <- viz_results
}
```

### Selected Subgroup Features + Estimated Thresholds + Estimated Subgroup ATEs

```{r}
sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP"
)
plt <- purrr::map(
  sim_names,
  function(sim_name) {
    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
    plt_selection <- plt +
      ggplot2::guides(
        color = ggplot2::guide_legend(nrow = 1),
        fill = ggplot2::guide_legend(nrow = 1)
      )
    
    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
    plt_cate <- plt +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12),
        legend.title = ggplot2::element_text(face = "bold", size = 16),
        legend.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(
        color = ggplot2::guide_legend(nrow = 1),
        fill = ggplot2::guide_legend(nrow = 1)
      )
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .var == "X1"
      )
    plt_thr1 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(1), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none")
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .var == "X2"
      )
    plt_thr2 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(2), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none")
    plt_thr <- plt_thr1 + plt_thr2
    
    plt <- patchwork::wrap_plots(
      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
      widths = c(3.5, 2.35, 1)
    ) &
      ggplot2::labs(x = NULL, color = "# of Repeated Crossfits") &
      ggplot2::theme(
        legend.position = "bottom",
        legend.box.margin = ggplot2::margin(t = 6, r = 0, b = 0, l = 0)
      )
    
    if (sim_name != sim_names[3]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[3] ~ 0.66
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.03, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    if (sim_name == sim_names[3]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_nreps_crossfit.pdf"),
  height = 9.5, 
  width = 15
)
```

## Rulefit Simulations

```{r results = "asis"}
sim_results_dir <- file.path(RESULTS_DIR, "Rulefit Simulations")
SIM_NAMES <- c(
  "AND DGP" = "AND DGP",
  "Additive DGP" = "Additive DGP",
  "OR DGP" = "OR DGP",
  "AND with Linear Covariates DGP" = "AND DGP with Linear Covariates",
  "Additive with Linear Covariates DGP" = "Additive DGP with Linear Covariates",
  "OR with Linear Covariates DGP" = "OR DGP with Linear Covariates"
)

# load in results
eval_results_ls <- list()
viz_results_ls <- list()
for (sim_name in names(SIM_NAMES)) {
  eval_results <- readRDS(
    file.path(
      sim_results_dir, sim_name, "Varying tau_heritability", "eval_results.rds"
    )
  )
  viz_results <- visualize_experiment(
    rulefit_experiment, NULL, eval_results
  )
  eval_results_ls[[SIM_NAMES[[sim_name]]]] <- eval_results
  viz_results_ls[[SIM_NAMES[[sim_name]]]] <- viz_results
}
```

### Selected Subgroup Features + Estimated Thresholds + Estimated Subgroup ATEs

```{r}
KEEP_METHODS <-  c(
  "CART",
  "Rulefit (linear + rules, max depth = 3)",
  "Rulefit (linear + rules, max depth = 2)",
  "Rulefit (rules only, max depth = 3)",
  "Rulefit (rules only, max depth = 2)"
)

sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND DGP with Linear Covariates",
  "Additive DGP with Linear Covariates",
  "OR DGP with Linear Covariates"
)
plt <- purrr::map(
  sim_names,
  function(sim_name) {
    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_selection <- plt
    
    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_cate <- plt +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12),
        legend.title = ggplot2::element_text(face = "bold", size = 16),
        legend.text = ggplot2::element_text(size = 12)
      )
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X1"
      )
    plt_thr1 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(1), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X2"
      )
    plt_thr2 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(2), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    plt_thr <- plt_thr1 + plt_thr2
    
    plt <- patchwork::wrap_plots(
      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
      widths = c(3.5, 2.35, 1)
    ) &
      ggplot2::labs(x = NULL) &
      ggplot2::theme(
        legend.position = "bottom",
        legend.box.margin = ggplot2::margin(t = 6, r = 0, b = 0, l = 0)
      )
    
    if (sim_name != sim_names[length(sim_names)]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none", linetype = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[6] ~ 0.6,
      TRUE ~ 0.5
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    if (stringr::str_detect(sim_name, "with")) {
      tag_x_pos <- -.08
    } else {
      tag_x_pos <- -.03
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(tag_x_pos, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.78, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    if (sim_name == sim_names[length(sim_names)]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 1.95, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_all_rulefit.pdf"),
  height = 17, 
  width = 15
)
```

## Correlated Simulations {.tabset .tabset-pills .tabset-pills-square}

```{r results = "asis"}
sim_results_dir <- file.path(RESULTS_DIR, "Correlated Simulations")
SIM_NAMES <- c(
  "AND with Correlated Linear Covariates DGP" = "AND DGP with Correlated Covariates",
  "Additive with Correlated Linear Covariates DGP" = "Additive DGP with Correlated Covariates",
  "OR with Correlated Linear Covariates DGP" = "OR DGP with Correlated Covariates"
)

# load in results
eval_results_ls <- list()
viz_results_ls <- list()
for (sim_name in names(SIM_NAMES)) {
  print(sim_name)
  experiment <- readRDS(
    file.path(
      sim_results_dir, sim_name, "Varying .X_corr", "experiment.rds"
    )
  )
  fit_results <- get_cached_results(experiment, "fit")
  eval_results <- get_cached_results(experiment, "eval")
  viz_results <- visualize_experiment(experiment, fit_results, eval_results)
  eval_results_ls[[SIM_NAMES[[sim_name]]]] <- eval_results
  viz_results_ls[[SIM_NAMES[[sim_name]]]] <- viz_results
}
```

### Selected Subgroup Features + Threshold Distances + Estimated Subgroup ATEs

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Causal Forest",
  "Distilled BCF",
  "Distilled Rspline",
  "Virtual Twins",
  "Causal Tree",
  "Linear Regression",
  "Lasso"
)

## with covariates
sim_names <- c(
  "AND DGP with Correlated Covariates",
  "Additive DGP with Correlated Covariates",
  "OR DGP with Correlated Covariates"
)
plt <- purrr::map(
  sim_names,
  function(sim_name) {
    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_selection <- plt
    
    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_cate <- plt +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12),
        legend.title = ggplot2::element_text(face = "bold", size = 16),
        legend.text = ggplot2::element_text(size = 12)
      )
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X1"
      )
    plt_thr1 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(1), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    
    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X2"
      )
    plt_thr2 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(2), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    plt_thr <- plt_thr1 + plt_thr2
    
    plt <- patchwork::wrap_plots(
      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
      widths = c(3.5, 2.35, 1)
    ) &
      ggplot2::labs(x = NULL) &
      ggplot2::theme(
        legend.position = "bottom",
        legend.box.margin = ggplot2::margin(t = 6, r = 0, b = 0, l = 0)
      )
    
    if (sim_name != sim_names[3]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none", linetype = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[3] ~ 0.66
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.08, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1,
          margin = ggplot2::margin(b = 16)
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1,
          margin = ggplot2::margin(b = 16)
        )
      )
    if (sim_name == sim_names[3]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_correlated_subgroup_errors_cov.pdf"),
  height = 9.5, 
  width = 15.5
)
```

## Causal Tree Experiments

```{r}
sim_results_dir <- file.path(RESULTS_DIR, "Causal Tree Simulations (cp=%s)")
SIM_NAMES <- c(
  "AND DGP" = "AND DGP",
  "Additive DGP" = "Additive DGP",
  "OR DGP" = "OR DGP",
  "AND with Linear Covariates DGP" = "AND DGP with\nLinear Covariates",
  "Additive with Linear Covariates DGP" = "Additive DGP with\nLinear Covariates",
  "OR with Linear Covariates DGP" = "OR DGP with\nLinear Covariates"
)
cps <- c(0, 1e-5, 1e-4, 1e-3, 1e-2, 1e-1)
eval_results_ls <- NULL
# cdt_eval_results_ls <- NULL
for (sim_name in names(SIM_NAMES)) {
  for (cp in cps) {
    experiment <- readRDS(
      file.path(
        sprintf(sim_results_dir, cp), sim_name, "Varying n", "experiment.rds"
      )
    )
    eval_results <- get_cached_results(experiment, "eval") |>
      purrr::map(~ .x |> dplyr::mutate(cp = !!cp))
    eval_results_ls <- c(eval_results_ls, list(eval_results))
  }
}

# subgroup
feature_selection_df <- purrr::map(
  eval_results_ls, "Subgroup Feature Selection Errors Summary"
) |>
  dplyr::bind_rows() |>
  dplyr::filter(
    .metric %in% c("nsubgroups", "F1", "tp", "fp")
  ) |>
  dplyr::mutate(
    .metric = dplyr::case_when(
      .metric == "nsubgroups" ~ "# Subgroups",
      .metric == "tp" ~ "# True Positives",
      .metric == "fp" ~ "# False Positives",
      TRUE ~ .metric
    ) |>
      factor(
        levels = c(
          "# Subgroups", "F1", "# True Positives", "# False Positives"
        )
      ),
    cp = dplyr::case_when(
      cp == 1e-1 ~ "1e-1",
      # cp == 1e-2 ~ "1e-2 (rpart default)",
      cp == 1e-2 ~ "1e-2*",
      cp == 1e-3 ~ "1e-3",
      cp == 1e-4 ~ "1e-4",
      cp == 1e-5 ~ "1e-5",
      TRUE ~ as.character(cp)
    ),
    .prune_mode = ifelse(
      stringr::str_detect(.method_name, "unpruned"), "Unpruned", "Pruned"
    ),
    .method_name = dplyr::case_when(
      .method_name %in% c("Causal Tree", "Causal Tree (unpruned)") ~
        sprintf("Causal Tree (cp = %s)", cp),
      TRUE ~ .method_name
    ) |>
      factor(
        levels = c(
          "Distilled Causal Forest", 
          sprintf("Causal Tree (cp = %s)", c("1e-1", "1e-2*", "1e-3", "1e-4", "1e-5", "0"))
        )
      )
  )

plt_ls <- list()
for (dgp_name in unique(feature_selection_df$.dgp_name)) {
  plt_ls[[dgp_name]] <- feature_selection_df |>
    dplyr::filter(
      .dgp_name == !!dgp_name,
      # .method_name != "Causal Tree (unpruned)"
    ) |>
    ggplot2::ggplot() +
    ggplot2::aes(
      x = n, 
      y = mean_feature_selection_err, 
      color = .method_name,
      linetype = .prune_mode
    ) +
    ggplot2::geom_ribbon(
      ggplot2::aes(
        x = n, 
        ymin = mean_feature_selection_err - se_feature_selection_err,
        ymax = mean_feature_selection_err + se_feature_selection_err,
        fill = .method_name,
        linetype = .prune_mode
      ),
      inherit.aes = FALSE,
      alpha = 0.4
    ) +
    ggplot2::geom_line() +
    ggplot2::geom_point() +
    ggplot2::facet_wrap(
      ~ .metric, scales = "free_y", strip.position = "left", nrow = 1
    ) +
    ggplot2::scale_color_manual(
      values = c("black", scales::hue_pal()(6))
    ) +
    ggplot2::scale_fill_manual(
      values = c("black", scales::hue_pal()(6))
    ) +
    ggplot2::labs(
      x = "Sample Size", y = SIM_NAMES[dgp_name], 
      color = "Method", fill = "Method", linetype = "Pruning Mode"
    ) +
    vthemes::theme_vmodern() +
    ggplot2::theme(
      strip.background = ggplot2::element_blank(),
      strip.placement = "outside",
      strip.text = ggplot2::element_text(
        color = "black", face = "bold", size = 16
      ),
      axis.title.y = ggplot2::element_text(face = "italic", size = 16),
      axis.text = ggplot2::element_text(size = 12),
      axis.title.x = ggplot2::element_text(face = "bold", size = 16),
      legend.title = ggplot2::element_text(face = "bold", size = 16),
      legend.text = ggplot2::element_text(size = 12)
    )
}
plt <- patchwork::wrap_plots(plt_ls, guides = "collect", ncol = 1) +
  patchwork::plot_layout(axes = "collect_x")
ggplot2::ggsave(
  filename = file.path(FIG_DIR, "causal_tree_tuning.pdf"),
  plt, 
  width = 16, height = 14
)
```

## Timing Experiments

```{r}
sim_results_dir <- file.path(
  RESULTS_DIR, "Timing Simulations", "Additive with Linear Covariates DGP"
)
experiment <- readRDS(file.path(sim_results_dir, "Varying n", "experiment.rds"))
fit_results <- get_cached_results(experiment, "fit")
timing_results <- readRDS(file.path(sim_results_dir, "timing_results.rds"))
legend_labels <- c(
  "time_elapsed" = "Full CDT Method (with Teacher Selection)",
  "time_elapsed_stability" = "Teacher Selection Method Only",
  "time_elapsed_student" = "Student Fit",
  "time_elapsed_jaccard" = "JaccardSSI"
)
legend_colors <- c(
  "time_elapsed" = "black",
  "time_elapsed_stability" = "#C7AD46",
  "time_elapsed_student" = "#2DA86A",
  "time_elapsed_jaccard" = "#614D96"
)

timing_df <- fit_results |>
  dplyr::mutate(
    time_elapsed = time_elapsed / 60,
    time_elapsed_student = timing_results$student_times,
    time_elapsed_stability = timing_results$stability_times / 60,
    time_elapsed_jaccard = timing_results$jaccard_times
  ) |>
  tidyr::pivot_longer(
    cols = tidyselect::starts_with("time_elapsed"),
    names_to = ".what",
    values_to = ".time_elapsed"
  ) |>
  dplyr::group_by(
    .dgp_name, .method_name, n, .what
  ) |>
  dplyr::summarise(
    mean_time = mean(.time_elapsed, na.rm = TRUE),
    se_time = sd(.time_elapsed, na.rm = TRUE) /
      sqrt(sum(!is.na(.time_elapsed))),
    .groups = "drop"
  )
main_timing_plt <- timing_df |>
  dplyr::filter(
    .what %in% c("time_elapsed", "time_elapsed_stability")
  ) |>
  ggplot2::ggplot() +
  ggplot2::aes(
    x = n, y = mean_time, color = .what
  ) +
  ggplot2::geom_ribbon(
    ggplot2::aes(
      x = n, 
      ymin = mean_time - se_time, 
      ymax = mean_time + se_time, 
      fill = .what
    ),
    inherit.aes = FALSE,
    alpha = 0.2
  ) +
  ggplot2::geom_line(linewidth = 1.5) +
  ggplot2::geom_point(size = 3) +
  ggplot2::scale_color_manual(labels = legend_labels, values = legend_colors) +
  ggplot2::scale_fill_manual(labels = legend_labels, values = legend_colors) +
  ggplot2::labs(
    x = "Sample Size (n)", y = "Mean Time Elapsed (minutes)", color = ""
  ) +
  vthemes::theme_vmodern(
    size_preset = "large",
    plot.tag = ggplot2::element_text(size = 18, face = "italic")
  ) +
  ggplot2::guides(fill = "none")
small_timing_plt <- timing_df |>
  dplyr::filter(
    .what %in% c("time_elapsed_jaccard", "time_elapsed_student")
  ) |>
  ggplot2::ggplot() +
  ggplot2::aes(
    x = n, y = mean_time, color = .what
  ) +
  ggplot2::geom_ribbon(
    ggplot2::aes(
      x = n, 
      ymin = mean_time - se_time, 
      ymax = mean_time + se_time, 
      fill = .what
    ),
    inherit.aes = FALSE,
    alpha = 0.2
  ) +
  ggplot2::geom_line(linewidth = 1.5) +
  ggplot2::geom_point(size = 3) +
  ggplot2::scale_color_manual(labels = legend_labels, values = legend_colors) +
  ggplot2::scale_fill_manual(labels = legend_labels, values = legend_colors) +
  ggplot2::labs(
    x = "Sample Size (n)", y = "Mean Time Elapsed (seconds)", color = ""
  ) +
  vthemes::theme_vmodern(
    size_preset = "large",
    plot.tag = ggplot2::element_text(size = 18, face = "italic")
  ) +
  ggplot2::guides(fill = "none")
plt <- patchwork::wrap_plots(small_timing_plt, main_timing_plt) +
  patchwork::plot_annotation(tag_levels = "A", tag_prefix = "(", tag_suffix = ")")
ggplot2::ggsave(
  filename = file.path(FIG_DIR, "timing_plot.pdf"),
  plt,
  width = 16, height = 5
)
```

## AIDs Case Study

```{r}
sim_results_dir <- file.path(RESULTS_DIR, "AIDS")
experiment <- readRDS(file.path(sim_results_dir, "experiment.rds"))
fit_results <- get_cached_results(experiment, "fit")

cdt_cf_out <- list(
  student_fit = list(
    fit = fit_results$fit[[
      which(fit_results$.method_name == "Distilled Causal Forest")
    ]]$min
  ),
  estimate = fit_results$group_cates[[
    which(fit_results$.method_name == "Distilled Causal Forest")
  ]]$min,
  stability_diagnostics = fit_results$stability_diagnostics[[
    which(fit_results$.method_name == "Distilled Causal Forest")
  ]]
)
cdt_rboost_out <- list(
  student_fit = list(
    fit = fit_results$fit[[
      which(fit_results$.method_name == "Distilled Rboost")
    ]]$min
  ),
  estimate = fit_results$group_cates[[
    which(fit_results$.method_name == "Distilled Rboost")
  ]]$min,
  stability_diagnostics = fit_results$stability_diagnostics[[
    which(fit_results$.method_name == "Distilled Rboost")
  ]]
)

tree_fit_results <- fit_results |>
  dplyr::filter(
    .method_name %in% c("Distilled Causal Forest", "Distilled Rboost", "Causal Tree")
  )
ssi_df <- purrr::map(
  tree_fit_results |>
    dplyr::pull(stability_diagnostics) |>
    setNames(tree_fit_results$.method_name),
  function(cdt) {
    tibble::tibble(
      tree_depth = 1:length(cdt$jaccard_mean),
      jaccard_ssi = cdt$jaccard_mean,
      jaccard_ssi_se = purrr::map_dbl(
        cdt$jaccard_distribution, 
        ~ sd(.x) / sqrt(length(.x))
      )
    )
  }
) |>
  dplyr::bind_rows(.id = "teacher_model")
jaccard_plt <- ggplot2::ggplot(ssi_df) +
  ggplot2::aes(x = tree_depth, y = jaccard_ssi, color = teacher_model) +
  ggplot2::geom_ribbon(
    ggplot2::aes(
      x = tree_depth,
      ymin = jaccard_ssi - jaccard_ssi_se,
      ymax = jaccard_ssi + jaccard_ssi_se,
      fill = teacher_model
    ),
    inherit.aes = FALSE,
    alpha = 0.2
  ) +
  ggplot2::geom_line() +
  ggplot2::geom_point() +
  ggplot2::scale_color_manual(values = COLORS) +
  ggplot2::scale_fill_manual(values = COLORS) +
  ggplot2::labs(
    x = "Tree Depth", y = "Jaccard SSI", 
    color = "Teacher Model", fill = "Teacher Model"
  ) +
  vthemes::theme_vmodern(size_preset = "large")
# jaccard_plt <- causalDT::plot_jaccard(
#   `Distilled Causal Forest` = cdt_cf_out, 
#   `Distilled Rboost` = cdt_rboost_out
# )
ggplot2::ggsave(
  jaccard_plt,
  filename = file.path(FIG_DIR, "aids_jaccard.pdf"),
  width = 7, height = 3.5
)

cdt_plt <- causalDT::plot_cdt(cdt_rboost_out)
ggplot2::ggsave(
  cdt_plt,
  filename = file.path(FIG_DIR, "aids_tree.pdf"),
  width = 9, height = 5
)

# cdt_rboost_out$estimate |>
#   dplyr::mutate(
#     se = sqrt(variance)
#   ) |>
#   dplyr::relocate("se", .after = "estimate") |>
#   View()
```

```{r}
sim_results_dir <- file.path(RESULTS_DIR, "AIDS (stability)")
experiment <- readRDS(file.path(sim_results_dir, "experiment.rds"))
fit_results <- get_cached_results(experiment, "fit")
eval_results <- get_cached_results(experiment, "eval")
viz_results <- visualize_experiment(experiment, fit_results, eval_results)

KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Causal Forest",
  "Virtual Twins",
  "Causal Tree",
  "Linear Regression",
  "Lasso"
)

jaccard_plt <- viz_results$`Subgroup Stability Diagnostics Plot`[[1]] +
  vthemes::theme_vmodern(size_preset = "large")
ggplot2::ggsave(
  jaccard_plt,
  filename = file.path(FIG_DIR, "aids_jaccard_stability.pdf"),
  width = 9, height = 5
)

plt <- eval_results$`Thresholds Summary` |>
  dplyr::filter(
    .method_name %in% !!KEEP_METHODS
  ) |>
  tidyr::pivot_wider(
    id_cols = c(.dgp_name, .method_name),
    names_from = .var,
    values_from = n_trees, 
    values_fill = 0
  ) |>
  tidyr::pivot_longer(
    cols = -c(.dgp_name, .method_name),
    names_to = ".var",
    values_to = "n_trees"
  ) |>
  dplyr::mutate(
    prop_trees = n_trees / length(unique(fit_results$.rep)),
    .var = dplyr::case_when(
      .var == "cd80" ~ "CD8\nCount",
      .var == "drugs" ~ "IV Drug\nUse",
      .var == "hemo" ~ "Hemophilia",
      .var == "homo" ~ "Sexual\nPreference",
      .var == "karnof" ~ "Karnofsky\nScore",
      .var == "preanti" ~ "Previous\nTherapy",
      .var == "strat" ~ "ARV\nStrata",
      .var == "wtkg" ~ "Weight",
      TRUE ~ stringr::str_to_title(.var)
    ) |>
      factor(
        levels = c(
          "CD8\nCount", "Weight", "Previous\nTherapy", "Age", "Karnofsky\nScore",
          "Symptom", "Race", "ARV\nStrata", "Sexual\nPreference", "Gender",
          "Hemophilia", "IV Drug\nUse"
        )
      ),
    .method_name = factor(.method_name, levels = KEEP_METHODS)
  ) |>
  ggplot2::ggplot() +
  ggplot2::aes(
    x = .var, y = prop_trees, fill = .method_name
  ) +
  ggplot2::geom_bar(
    stat = "identity", position = "dodge"
  ) +
  ggplot2::scale_fill_manual(
    values = COLORS
  ) +
  ggplot2::labs(
    x = "Subgroup Variable", y = "Proportion Selected", fill = "Method"
  ) +
  vthemes::theme_vmodern(
    size_preset = "medium",
    legend.position = "bottom"
  )
ggplot2::ggsave(
  plt,
  filename = file.path(FIG_DIR, "aids_stability.pdf"),
  width = 10, height = 4
)
```
